Learning to Prove with Tactics

### 2018-03-28 presentation/presentation.tex
minor

\begin{center}
\begin{tabular}{lcc}
\toprule
  & 7164 \holfour theorems (60s) & 3329 \cakeml theorems (15s)\\
\midrule
   \eprover   & 2472 (34.5\%) & \phantom{0000 } 20.0\%?\\
   \tactictoe & 4760 (66.4\%) & 1161 (34.9\%)\\
\midrule
   Total  & 4946 (69.0\%) & \\
\bottomrule
\end{tabular}
\end{center}
\end{frame}

@@

add cakeml
\centering
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=\textwidth,
  height=0.7*\textwidth,
  ymin=0, ymax=2000,
  xmin=0, xmax=20,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\legend{\holfour}
\end{axis}
\end{tikzpicture}
\end{frame}

>>>>

\begin{center}
\begin{tabular}{lcc}
\toprule
  & \holfour: 7164, 60s & \cakeml: 3329, 15s\\
\midrule
   \eprover   & 2472 (34.5\%) & \\
   \tactictoe & 4760 (66.4\%) & 1161 (34.9\%)\\
\midrule
   Total  & 4946 (69.0\%) & \\
\bottomrule
\end{tabular}
\end{center}
\end{frame}

@@

\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.3*\textwidth,
  height=0.7*\textwidth,
  ymin=0, ymax=2000,
  xmin=0, xmax=15,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/original_proof_length};
\addplot table[x=length, y=proofs] {data/cakeml_original_proof_length};
\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.6*\textwidth,
  height=0.7*\textwidth,
  ymin=0, ymax=100,
  xmin=15, xmax=50,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/original_proof_length};
\addplot table[x=length, y=proofs] {data/cakeml_original_proof_length};
\legend{\holfour,\cakeml}
\end{axis}
\end{tikzpicture}
\end{frame}
